s How the representative set is computed; pruning strategies and
% verification step goes here.

\section{Computing Representative Sets}
 Representative vertex $v$ of a pattern vertex $u$ implies that there
 exists an approximate subgraph isomorphism $\phi$ for which $\phi(u) = v$.
 One way to interpret it is that the neighborhood of $u$ matches with
 that of $v$.  By comparing the neighborhoods we can find 
 vertices that are not valid representatives of $u$ without trying to
 find an isomorphism exhaustively. Therefore, to compute the
 representative sets we will start with a candidate 
 representative set denoted by \CR  and iteratively
 prune some of the vertices if the neighborhoods cannot be matched.
 The representative set is a superset of the candidate set $\CR \supseteq \RS$.
 and $\vg \supseteq \RS$ is one such example.
  In this section, we will
 describe different notions of neighborhood and show how they
 help us in computing the representative
 sets. \\
The problem of checking whether a vertex $v \in R(u)$
 involves solving
 approximate subgraph isomorphism which is a NP complete
 problem. The pruning methods therefore 
 typically cannot prune all the invalid
 candidate vertices. 
 So, we use an exhaustive enumeration method to prune the remaining
invalid vertices and obtain the set of representative
vertices.

 \subsection{\khop Label}
 %Neighbors of a vertex in a graph denotes the set of vertices that are
 %reachable via a single edge. 
 \khop label 
 is the set of vertices that are reachable via a simple
 path of length $k$. 
 Note that, we use the word label even though we refer to a set of vertices.
 Formally, the \khop label of a vertex
 $v$ in graph $G$, $\khopl{k}{v,G} = \{u | u \in G, \kpath{u}{v}{k}\}$.
 We simply write it as $\khopl{k}{v}$ when the graph is evident from
 the context. 
For example, for pattern $P$ in
Fig.~\ref{subfig:pattern}, the $0$-hop label of vertex $5$ is $h_0(5)
 = \{5\}$, its $1$-hop label is the multiset $h_1(5) = \{2, 4, 6\}$ 
 and its $2$-hop label $h_2(5) = \{1, 3\}$. The minimum 
 cost of matching \khop labels
 $\khopl{k}{u}$ and $\khopl{k}{v}$ is equal to 

 \begin{equation}
  \khopcost{k}{u}{v} = \text{min}\displaystyle\sum_{u' \in \khopl{k}{u}} \matij{C}{L(u')}{L(f(u'))}
 \end{equation}

where 
$\matij{C}{L(u')}{L(f(u'))}$ is the cost of matching the vertex labels and
$f$ is an injective function $f\!\!:\khopl{k}{u} \rightarrow \khopl{k}{v}$.
In other words,
it is the minimum total cost of matching the vertices present in the \khop labels.
The following theorem places a upper bound on the minimum cost of matching
the \khop labels of pattern vertex and its representative vertex.

\begin{thm}
Given any pattern vertex $u$, a representative vertex $v \in R(u)$ and cost
threshold $\alpha$, the minimum cost of matching the \khop labels, 
$\khopcost{k}{u}{v} \leq \alpha$ for all $k \geq 0$.

\begin{myproof}
Consider any approximate subgraph isomorphism $\phi$
such that $\phi(u) = v$. It is enough if we can show an injective function
$f\!\!:\khopl{k}{u} \rightarrow \khopl{k}{v}$ with a cost
$\leq \alpha$. We will argue that the function $\phi$ on the restricted domain
$\khopl{k}{u}$ is one such function $f$.
First, we know that 
$\sum\matij{C}{L(u)}{\phi(L(u)} \leq \alpha$, for all $u \in \vp$ since
$\phi$ is an approximate subgraph isomorphism. Second, let 
$\kpath{u}{u'}{k}$
then $\phi(u') \in \khopl{k}{v}$ because for every edge $(u_1, u_2)$ on a 
path between $u$ and $u'$ in $\pat$, $(\phi(u_1),\phi(u_2)) \in \eg$. 
Therefore the minimum cost of matching the \khop labels is upper bounded
by $\alpha$.
\end{myproof}
\label{thm:khop}
\end{thm}

Based on the above theorem, a vertex $v$ can be pruned from 
\CR if $\khopcost{k}{u}{v} > \alpha$ for any 
$k \geq 0$. However, in practice, it enough to check the condition only
for $k \leq |V_P|-1$ because $\khopl{k}{u}$ is the null set $\forall k \geq
|V_P|$ and the condition is trivially satisfied.

Figure~\ref{fig:ncexample} shows an example for the \khop label based
pruning of the representative set where the
threshold $\alpha = 0.5$. Consider vertex $2 \in \vp$ and vertex
$20 \in \vg$, we have 
$\khopcost{0}{2}{20} = 0$, since the cost of matching vertex labels 
\matij{C}{C}{C} = 0, 
as per the label matching matrix
\M{C} in Fig.~\ref{subfig:match}. The \khop labels for $k=1,2,3$ and 
the minimum of cost matching them are
as shown in the table \ref{tab:khop220}, and it can be verified that
the minimum cost is within the threshold $\alpha$.

Thus far, we cannot prune node $20$ from $R'(2)$.
However, $\khopl{4}{2}
= 4, 5 $ and $\khopl{4}{20} = 30, 60$ and the minimum cost of matching
them is $0.6 > \alpha$.
Thus, we conclude that $20
\notin R'(2)$. This small example illustrates that \khop labels can help
prune the candidate representative sets.


% Example for showing the incremental updates of the labels
\begin{figure}[!ht]
\captionsetup[subfloat]{captionskip=15pt}
  \centering
  \subfloat[Pattern $P$]{
    \label{subfig:pattern}
	\scalebox{0.9}{
    % # 3 vertices and 2 edge pattern
    \begin{pspicture}(0,0)(4,3)
    \cnodeput[linecolor=black](0,2) {n1} {A}
    \cnodeput[linecolor=black](0,1) {n2} {C}
    \cnodeput[linecolor=black](1,0) {n3} {B}
    \cnodeput[linecolor=black](2,2) {n4} {C}
    \cnodeput[linecolor=black](2,1) {n5} {A}
    \cnodeput[linecolor=black](2,0) {n6} {D}
    %% Draw the edges of the pattern
  \ncline{-}{n1}{n2}
  \ncline{-}{n2}{n3}
  \ncline{-}{n3}{n4}
  \ncline{-}{n2}{n5}
  \ncline{-}{n4}{n5}
  \ncline{-}{n5}{n6}
  \ncline{-}{n3}{n6}
    \uput{.3cm}[90](n1){ {1} }
    \uput{.3cm}[180](n2){ {2} }
    \uput{.3cm}[270](n3){ {3} }
    \uput{.3cm}[90](n4){ {4} }
    \uput{.3cm}[0](n5){ {5} }
    \uput{.3cm}[270](n6){ {6} }
    \end{pspicture}
	} }
  \subfloat[Database Graph $G$]{
    \label{subfig:database}
	\scalebox{0.9}{
    \begin{pspicture}(0,0)(2.5,2.5)
    \cnodeput[linecolor=black](0,2) {N1} {A}
    \cnodeput[linecolor=black](0,1) {N2} {C}
    \cnodeput[linecolor=black](0,0) {N3} {D}
    \cnodeput[linecolor=black](1,2) {N4} {B}
    \cnodeput[linecolor=black](2.25,1) {N5} {B}
    \cnodeput[linecolor=black](2,0) {N6} {A}
    % vertex ids
    \uput{.3cm}[90](N1){ {10} }
    \uput{.3cm}[180](N2){ {20} }
    \uput{.3cm}[270](N3){ {30} }
    \uput{.3cm}[90](N4){ {40} }
    \uput{.3cm}[0](N5){ {50} }
    \uput{.3cm}[270](N6){ {60} }
    % edges in the database
  \ncline{-}{N1}{N2}
  \ncline{-}{N2}{N3}
  \ncline{-}{N4}{N5}
  \ncline{-}{N5}{N6}
  \ncline{-}{N3}{N4}
  \ncline{-}{N2}{N5}
  \ncline{-}{N2}{N6}
    \end{pspicture}
	} }
  \newline
\captionsetup[subfloat]{captionskip=5pt}
\subfloat[Cost Matrix]{
  \label{subfig:match}
  % Table for the search space pruning
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    \Cs & A &  B & C & D \\
    \hline
    A & 0 & 0.7 & 0.6 & 0.1\\
    \hline
    B & 0.7 & 0 & 0.3 & 1\\
    \hline
    C & 0.6 & 0.3 & 0 & 0.8\\
    \hline
    D & 0.1 & 1 & 0.8 & 0\\
    \hline
  \end{tabular}
  } 
  \caption{Pattern \protect\subref{subfig:pattern}, 
  database graph \protect\subref{subfig:database}, and binary cost
  matrix \protect\subref{subfig:match}.
  } 
  \label{fig:ncexample}
\end{figure}

\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
        k & $\khopl{k}{2}$ & $\khopl{k}{20}$ & $\khopcost{k}{2}{20}$\\
        \hline
        1 & 1, 3, 5 & 10, 30, 50, 60 & 0 \\
        2 & 4, 6 & 40, 50, 60 & 0.4 \\
        3 & 3, 5 & 40, 30, 50 & 0.1\\
        \hline
    \end{tabular}
    \caption{\khop label of vertices $2$ and $20$}
    \label{tab:khop220}
\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
        k & $h_k(3)$ & $h_k(50)$ & $\khopcost{k}{3}{50}$ \\
        \hline
        0 & 3 & 50 & $0$\\
        1 & 2, 4, 6 & 20, 40, 60 & $0.4$ \\
        2 & 1, 5 & 10, 20 , 30, 60 & 0\\
        3 & 2, 4, 5 & 10, 20, 30, 40 & $0.3$ \\
        4 & $1$ & $10, 40, 60$ & $0$ \\
        \hline
    \end{tabular}
    \caption{\khop labels of vertices $3$ and $50$.}
    \label{tab:khop350}
\end{table}


\smallskip\noindent{\bf Precomputing \khop labels for $G$:} The \khop
labels of the database vertices are independent of the pattern. Thus, we
can precompute the \khop labels for different values of $k$.


One way to find the \khop label is by naively
enumerating all the $k$ length paths.
Hence, we compute the \khop labels only for small values of $k$ depending on the
database size and density. 





\subsection{Neighbor Concatenated Label} 
In a given iteration of Neighbor concatenated label (\ncl) based pruning,
the information regarding the candidates of a neighbor that were pruned 
in the previous iteration is used along with the current \khop label to
prune candidates in the current iteration. In contrast, the \khop label
pruning strategy for a vertex $u$ works independently of the result of
\khop label pruning of other vertices in the pattern. This leads us
to the following recursive formulation for \ncl.

The \ncl of a vertex in the ${k+1}^{th}$ iteration, $\nclab{k+1}{u}$ is
defined as
the tuple $(\{\nclab{k}{u'} | u' \in N(u)\},\xspace \khopl{k+1}{u})$.
The first element(A) of the tuple is the \ncl of the neighbors of the
vertex $u$ in the previous iteration and the second element(B) is exactly
same as the \khop label defined in the previous section. We say that
$\nclab{k+1}{v}$ dominates $\nclab{k+1}{v}$, denoted by 
$\nclab{k+1}{u} = (A, B) \preceq \nclab{k+1}{v} = (A', B') $ 
iff $\khopcost{k+1}{B}{B'} \leq \alpha$ and there exits an injective
function $g\!\!:A\rightarrow A'$ such that $a \leq g(a)$ for 
all $a \in A$. The base case $\nclab{0}{u} \preceq \nclab{0}{v}$ iif 
$\khopcost{0}{u}{v} \leq \alpha$. For example, in Fig~\ref{fig:ncexample} 
$\nclab{1}{2} \preceq \nclab{1}{20}$ because $\khopcost{1}{2}{20} \leq \alpha$
and the injective function that maps neighbors $1, 3, 5$ of $2$ to neighbors
$10, 50, 30$ of $20$ such that $\preceq$ relation is
is satisified between every pair. The following theorem states that the \ncl of a pattern
vertex $u$ is dominated by the \ncl of any of its representative vertex
$v \in R(u)$.

\begin{thm}
Given any pattern vertex $u$, a representative vertex $v \in R(u)$ and cost
threshold $\alpha$, $\nclab{k}{u} \preceq \nclab{k}{v}$ for all
$k \geq 0$.
\begin{myproof} Let $\phi$ be any approximate subgraph isomorphism
such that $\phi(u) = v$.
We prove the theorem by using the principle of mathematical induction on $k$.\\
\textbf{Base case:} $\nclab{0}{u} \preceq \nclab{0}{v}$ is true because
$v \in R(u)$. \\
\textbf{Inductive Hypothesis:} Assume that $\nclab{k}{u} \preceq \nclab{k}{v}$
holds true for all $u \in \pat$ and $v \in R(u)$. \\
Now consider 
$\nclab{k+1}{u} = (A, B)$  and $ \nclab{k+1}{v} = (A', B') $, from theorem
\ref{thm:khop} we know that $\khopcost{k+1}{B}{B'} \leq \alpha$, for all
$k \geq 0$. The injective function $\phi$ maps the elements $a \in A'$ to
elements in $\phi(a)$ and $\phi(a) \in A'$ from the inductive hypothesis.
The theorem follows from the definition of the \ncl label.
\end{myproof}
\label{thm:ncl}
\end{thm}

Based on the above theorem, a vertex $v$ can be pruned from 
\CR if $\nclab{k}{u} \not\preceq \nclab{k}{v}$
for some $k \geq 0$. In Fig~\ref{fig:ncexample} , consider the vertices
$3 \in \pat$ and $50 \in \db$. The \ncl labels, 
$\nclab{0}{3} \preceq \nclab{0}{50}$ as $\matij{C}{B}{B} = 0 \leq \alpha$.
Similarly it is also true for the pairs $(2, 20)$, $(4, 40)$ etc. It follows
that $\nclab{1}{3} \preceq \nclab{1}{50}$ as the neighbors can be mapped and
the minimum cost of the \khop label is within the $\alpha$ threshold. But
$\nclab{2}{3} \not\preceq \nclab{2}{50}$ because the \ncl label
$\nclab{1}{6}$ is not dominated by the \ncl label
of $20, 40$ or  $60$ in the previous iteration and so the
there is no mapping between the neighbors of vertices $3$ and 
$50$ in the current iteration. Hence, the vertex $50$
can be pruned from the candidate representative set of vertex $3$.
Note that using the \khop label in the same example will not prune the
vertex $50$ because the minimum cost of matching the \khop labels is within
$\alpha$ as shown in table \ref{tab:khop350}. Therefore, \ncl label is more
efficient compared to \khop label as it subsumes the latter label.

\subsection{Candidate set verification}
The pruning methods based on the \khop and the \ncl labels starts with a
\CR and prune some of the candidate vertices
based on the conditions described in theorems \ref{thm:khop} and \ref{thm:ncl}.
The verification step reduces \CR to \RS by pruning retaining only those vertices
for which there exists an approximate subgraph isomorphism $\phi$ in which $\phi(u) = v$.

Let $wp = u_0,\ldots, u_m$ be a walk in the pattern that covers each
edge of the pattern atleast once starting from vertex $u$ i.e. $u_0 = u$.
The following three conditions are satisfied iff the vertex $v$ is a
representative of the vertex $u$. i) there exists a walk $w_d = v_0,\ldots, v_m$
such that every $(v_i, v_{i+1})$ is such that $v_i \in R'(u_i)$ and
$v_{i+1} \in R'(u_{i+1})$. ii) $v_i = v_j$ implies that $u_i = u_j$. iii) 
$\sum\matij{C}{L(u_i)}{L(v_i)} \leq \alpha$ where $u_i \in \vp$. These 
conditions can be verified by following the definition of approximate
subgraph isomorphism. Using an example we will show how these conditions
are verified.

Consider checking whether the vertex $3$ is a valid representative of the 
vertex $10$ in the pattern in the figure~\ref{fig:ex1} and let 
$\alpha = 0.5$ . The walk $ w_p = 10, 20, 40, 30, 10$
covers each edge of the pattern atleast once. Any Walk that satisfies the
above three conditions should start mapping the vertex $10$ to $3$. The cost of 
matching the labels of vertices $3$ and $10$ is $0.2$ from the cost matrix.
We will cover the walk $w_p$ one edge at a time. For any $(u_i, u_{i+1})$ in the walk, 
if $u_i$ and $u_{i+1}$ are mapped already then we verify that there is 
an edge between the database vertices $v_i, v_{i+1}$ to which the pattern vertices are mapped.
If however, $u_{i+1}$ is not mapped already then we map it to some vertex in $v_{i+1} = R'(u_{i+1})$
and subtract the cost of this mapping from the remaining $\alpha$ cost.
For example, in the first step we can map $20$ to $2$. The remaining
cost is then $0.1$. In the next step $(20,30)$, the vertex $30$
cannot be mapped to any vertex in the database without violating the three conditions.
In such a case, we back track 1 step and choose a different mapping say $1$
for the vertex $20$ which is the last vertex that was mapped. Proceeding this way, we can arrive
at the mapping corresponding to $\phi_{1}$ as in table~\ref{subfig:ex_occur}.
This isomorphism not only guarantees that $3 \in R(10)$, it also implies
that the verfication check between the pairs $(20, 1), (30, 6)$ and $(40, 4)$
can be avoided becuase of the approximate isomorphism $\phi_1$ that was found.



\subsection{Label costs and dominance checking}
Candidate representative vertices are pruned by checking for dominance between
the \ncl labels which itself requires computing the cost between the \khop labels.
Both these tasks involve finding an injective function that tries to optimize
some objective function. These problems can be modelled as network flow problems
for which there are many efficient algorithms. 

\medskip{\textit{Computing \khop label cost}:} To compute the minimum
matching cost between the \khop labels
$\khopl{k}{u}$ and $\khopl{k}{v}$ we compute the maximum flow with minimum
cost in the flow network $F$ defined as follows. $F$ contains two groups of
vertices in addition to designated source and sink nodes. 
First group contains a node for
each label that appears on a vertex $u' \in \khopl{k}{u}$ and it is connected
to src node with zero weight and the capacity is equal to the number of vertices
in $\khopl{k}{u}$ that have the same vertex label as that of $u'$.
The second group contains nodes
for labels that are present on $v' \in \khopl{k}{v}$ and are connected sink 
node with a weight of $0$ and a capacity equal to the 
number of nodes in $\khopl{k}{v}$ that have the same label as
that of $v'$. The only other edges are those between the
vertices in different groups. Consider vertices corresponding to labels $l_u$
and $l_v$ in the two groups respectively. The weight of the edge is $\matij{C}{l_u}{l_v}$
and the infinite capacity.
The cost between the \khop labels is equal to
minimum cost for maximum flow if the total flow is equal to $|\khopl{k}{u}|$ and 
$\infty$ otherwise. \\
Figure~\ref{fig:Hflow} shows the flow network required to compute the minimum
cost of matching the \khop labels $\khopl{2}{2}$ and $\khopl{2}{20}$ as shown in
table \ref{tab:khop220}. The vertices connected to the source, $s$ correspond to
the graph labels of $\khopl{2}{2}$ and the vertices connected to the sink, $t$, 
correspond to the graph labels of $\khopl{2}{20}$. The numbers in the box represent
the capacity and the weight of the edges.
Note that the number of vertices connected to the sink is only $2$ 
is even though $|\khopl{2}{20}| = 3$ because the vertices $40$ and $50$
have the common graph label $B$. Vertex corresponding to $B$ is therefore
connected to $t$ with a capacity of $2$. The maximum flow in the network
is $2$ and the minimum cost of sending $2$ units of flow $0.4$ is 
achieved by pushing a unit flow along the paths $s, C, B, t$ and $a, D, A, t$.
Therefore, the cost of matching the labels $\khopl{2}{2}$ and $\khopl{2}{20}$
is $0.4$.

\medskip{\textit{Dominance check}: } The \khop label part of the \ncl label can
be compared using the above network flow formulation and matching the recursive
part of the \ncl label can be done using maximum bipartite matching. Consider 
$\nclab{k+1}{u} = (A, B)$ and $\nclab{k+1}{v} = (A', B')$, the 
exisitence of injective function between $A$ and $A'$ can be checked by computing 
the maximum matching in a bipartite graph with edges $(a, a')$ where $a \in A$ and
$a' \in A'$.
The \ncl label
$\nclab{k}{v}$ therefore dominates $\nclab{k}{u}$ if cost between the \khop labels is within
$\alpha$ and the size of maximum bipartite matching is $|N(u)|$.

\medskip{\textit{Optimization}: } Candidate pattern may contain groups of symmetric
vertices that are indistinguishable with respect to the \khop label. In such a scenario, 
the candidate representative sets of all these vertices are exactly the same. Utilizing the
symmetry, we apply the pruning strategy only on one vertex per symmetry group and 
replicate the results for all other vertices in the group. For example, the
vertices $10$ and $40$ in figure~\ref{subfig:ex_sub} are symmetric and
the representative sets $R'(10)$ and $R'(40)$ are exactly the same.
In abstract algebra terms such  
groups are called orbits of the graph and can be computed using nauty algorithm. Even though
computing the orbits is expensive, we can avoid $ (|g|-1) \times |\CR|$ \khop label cost computations
where $g$ is size of the orbit. Note that the payoff is zero if all the vertex orbits are of
size $1$.

\subsection{Precomputing database \khop labels}
The \khop label of the database vertices is independent of the candidate pattern. Hence, even though
computing the cost of matching the \khop labels using maximum flow is expensive, it
can be amortized over all the candidate patterns  if we precompute the \khop labels of the
database vertices. Also, to construct the flow network we only need the aggregate information
about the number of vertices of a given database label ( TODO) 
in the \khop label which can be stored in the main memory. 

\begin{thm}
k-reachable (KR) : Given a graph $G$, $k$ and $u \in \vg$. Compute $\khopl{k}{u}$.
k-reachable cannot be solved in polynomial time unless $P = NP$.

\begin{myproof}
We prove this by reducing hamiltonian path (HP) to KR.
Hamiltonian Path : Given a graph $G$, is there a simple path of length
$|\vg|-1$ i.e. is there a path that visits each and every vertex exactly
once. The problem of finding a Hamiltonian path is proven to be an NP-Complete
problem \cite{npcomplete}.\\
Assume that algorithm $X(k)$ can compute KR in polynomial time. Let $|\vg| = n$ 
and $u$ be starting vertex in HP if it exists.
Given an instance of HP, we first get a vertex $v$, $\kpath{u}{v}{n-1}$ using
$X(n-1)$. The vertex $v$ is removed from the graph and we find a vertex $v'$
such that $\kpath{u}{v'}{n-2}$ and $(v', v) \in \eg$. We repeat this process
$n-1$ times. If at any stage $X(j) = \{\}$ then we restart from a different starting
vertex. The vertices selected in each iteration lie on a path of length $n-1$ if it exists.
\end{myproof}
\end{thm}

To compute \khop label of a vertex $u$, we check for each vertex $v$ whether
$v \in \kpath{u}{v}{k}$ by enumerating all possible $k$ length
paths until a path is found.
This procedure is exponential, we therefore fix a maximum value $k_{max}$ and use
the \khop label based pruning only for values of $k \leq k_{max}$.
It only takes a couple of minutes to compute \khop label for 
$k \leq 6$ for all the vertices in the database graph. This is 
significantly less than the overall run time of the algorithm. Once 
$\khopl{k}{u}$ is computed we store in memory only the tuples $(m, l)$
where $m$ is the number of vertices $v \in \khopl{k}{u}$, $L(v) = l$.



\begin{figure}[!h]
    \centering
\scalebox{0.6}[0.6]{
  \psset{unit=0.85in}
  \newcommand\arc[4]{\ncline{#1}{#2}{#3}\ncput{\colorbox{gray!40}{#4}}}
      \begin{pspicture}(0,1)(5,3)
        \cnodeput[doubleline=true](1,2){src}{s}
        \cnodeput(2,1){n1}{C}
        \cnodeput(2,3){n2}{D}
        \cnodeput[doubleline=true](5,2){sink}{t}
        \cnodeput(4,1){n4}{B}
        \cnodeput(4,3){n5}{A}
        \arc{->}{src}{n1}{$1,0$}
        \arc{->}{src}{n2}{$1,0$}
        %\arc{->}{n1}{n4}{$1$}
        \ncline{->}{n1}{n4}\ncput[npos=0.5]{\colorbox{gray!40}{$\infty,0.1$}}
        \ncline{->}{n1}{n5}\ncput[npos=0.3]{\colorbox{gray!40}{$\infty,1$}}
        \ncline{->}{n2}{n4}\ncput[npos=0.3]{\colorbox{gray!40}{$\infty,0.6$}}
        \ncline{->}{n2}{n5}\ncput[npos=0.5]{\colorbox{gray!40}{$\infty.0.3$}}
        \arc{->}{n4}{sink}{$2,0$}
        \arc{->}{n5}{sink}{$1,0$}
        %\arc{->}{n6}{sink}{$1$}
      \end{pspicture}
    }
    \caption{Flow network for \khopl{2}{2} and \khopl{2}{20}}
	\label{fig:Hflow}
\end{figure}
